Clustering and Parameter Estimation for the Popularity Adjusted Block Model

### 2020-07-23 summary.Rmd
some comparisons done

In this part, we will assess Algorithm 2's performance for sample sizes 
$n = 64, 128, 256, 512, 1024$. For each sample size $n$, $100$ sets of 
$\lambda^{(kl)}$'s are drawn and for each set of parameters, one adjacency 
matrix $A$ is drawn and clustered.

We will not consider clustering using the edge probability matrix $P$ since 
this will always result exact recovery of the original clusters.

```{r fig.cap = 'IQR clustering error using Algorithm 1 for sample sizes from 64 to 1024. Simulations were repeated 100 times for each sample size.', cache = FALSE}
clustering.df <- readr::read_csv('clustering.csv')
clustering.df %>%
  dplyr::group_by(n) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75)) %>%
  ggplot() +
  # scale_y_log10() +
  labs(y = 'error') +
  geom_line(aes(x = n, y = med.err)) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q))
```

@@

Figure \ref{fig:lambda_est} shows the medians and interquartile ranges of root 
mean square errors for Algorithm 4 over 100 simulations using the same 
parameters as before.

```{r lambda_est, cache = FALSE, fig.cap = 'Median and IQR RMSE from Algorithm 4 using sample sizes from 64 to 1024. Simulations were repeated 100 times for each sample size.'}
rmse.df <- readr::read_csv('rmse.csv')

rmse.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(median.rmse = median(rmse),
                   q1.rmse = quantile(rmse, .25),
                   q3.rmse = quantile(rmse, .75)) %>% 
  dplyr::ungroup() %>% 
  ggplot() + 
  scale_y_log10() + 
  scale_x_log10() +
  geom_line(aes(x = n, y = median.rmse)) + 
  geom_errorbar(aes(x = n, ymin = q1.rmse, ymax = q3.rmse)) + 
  labs(y = 'RMSE')
```

>>>>

In this part, we will assess Algorithm 2's performance for sample sizes 
$n = 64, 128, 256, 512, 1024$. For each sample size $n$, $100$ sets of 
$\lambda^{(kl)}$'s are drawn and for each set of parameters, one adjacency 
matrix $A$ is drawn and clustered. We will not consider clustering using the 
edge probability matrix $P$ since this will always result exact recovery of the
original clusters (up to permutation).

```{r clust_err_sim, fig.cap = 'IQR clustering error using Algorithm 1 (red) compared against subspace clustering (blue) for sample sizes from 64 to 1024. Simulations were repeated 100 times for each sample size. The $y$-axis is shown on a logarithmic scale.', cache = FALSE}
clustering.df <- readr::read_csv('clustering.csv')
clustering.df %>%
  dplyr::group_by(n) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  scale_y_log10() +
  labs(y = 'clustering error', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'Algorithm 1')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'Algorithm 1')) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC')) + 
  scale_colour_brewer(palette = 'Set1')
```

@@

Figure \ref{fig:lambda_est} shows the medians and interquartile ranges of root 
mean square errors for Algorithm 4 over 100 simulations using the same 
parameters as before. Comparison against an MLE-based method 
\cite{noroozi2019estimation} suggests similar performance.

```{r lambda_est, cache = FALSE, fig.cap = 'Log-log plot of the median and IQR RMSE from Algorithm 4 (red) compared against an MLE-based method (blue) using sample sizes from 64 to 1024. Simulations were repeated 100 times for each sample size.'}
rmse.df <- readr::read_csv('rmse.csv')

rmse.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(median.rmse = median(rmse),
                   q1.rmse = quantile(rmse, .25),
                   q3.rmse = quantile(rmse, .75),
                   median.rmse.mle = median(rmse.mle),
                   q1.rmse.mle = quantile(rmse.mle, .25),
                   q3.rmse.mle = quantile(rmse.mle, .75)) %>% 
  dplyr::ungroup() %>% 
  ggplot() + 
  scale_y_log10() + 
  scale_x_log10() +
  geom_line(aes(x = n, y = median.rmse, colour = 'Algorithm 4')) + 
  geom_errorbar(aes(x = n, ymin = q1.rmse, ymax = q3.rmse,
                    colour = 'Algorithm 4')) + 
  geom_line(aes(x = n, y = median.rmse.mle, colour = 'MLE-based')) + 
  geom_errorbar(aes(x = n, ymin = q1.rmse.mle, ymax = q3.rmse.mle,
                   colour = 'MLE-based')) + 
  scale_colour_brewer(palette = 'Set1') + 
  labs(y = 'RMSE', colour = NULL)
```

# Discussion
